si: code and prose exploring Spatial Interaction models

### 2022-04-21 README.qmd
Change output variable name for #9
Former-commit-id: 68bf56d2039a28ccdd978670f21764ca145dd7a4

```{r distance}
library(si)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
# perform SIM
od_res = si_calculate(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
# visualize the results
plot(od_res$distance_euclidean, od_res$res)
```

>>>>

```{r distance}
library(si)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
# perform SIM
od_res = si_calculate(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```
